%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{lastcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Spencer Last}
\address{2011 S 2100 E, \#105 \linebreak Salt Lake City, UT 84108}
\contacts{(559) 269-2289 \linebreak spencerjlast@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Provo, UT}{Brigham Young University}{Jan 2011 -- Dec 2015}
			\begin{itemize}
				\item \textbf{B.S. in Computer Science}, Dec 2015. GPA: 3.46
				\item \textbf{Relevant Coursework:} Data Structures, Operating Systems, Algorithm Analysis, Software Design and Testing, Interactive Graphics, Internet Programming, Computer Communication and Networking, Machine Learning, Parallel Processing, Computer Security
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Developer}{Goldman Sachs}{Jan 2016 - Present}
			\begin{itemize}
			    \item Architected and implemented platform of microservices that act as middleware to Exchange which allowed automation of critical email processes for the entire firm.
			    \item Designed and built UI of tool suite that improves visibility of Exchange infrastructure health across the firm and reduces support by displaying statistics and best practice violations of individual user mailboxes and load balance across Exchange.
			    \item Saved millions of dollars per quarter by replacing legacy software that automated creation of shared mailboxes on a version of Exchange that ran on an end-of-support version of Windows Server.
				\item Developed service that fetches 11 performance counters from 197 Exchange servers within 60 seconds to identify unusual behavior in real time and prevent any undesired effects.
				\item Reduced failure rate of user mailbox delegate creation in the firm from 5.3\% to 1.6\% by designing and building services to replace end-of-life systems that automated delegate creation.
				\item \underline{Technologies applied} Full-stack development, web development using React.js and Redux.js, C\#.NET, PowerShell, micro-services built with Java Spring Boot and Node.js in TypeScript, BPMN workflow modeling, Postgres SQL, SVN, Git, Agile
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Back End Software Developer}{BYU Broadcasting}{Aug 2015 -- Dec 2015}	
			\begin{itemize}
				\item Built back end services for BYU Broadcasting web UIs.
				\item \underline{Technologies applied} C\#.NET, MS SQL Server, stored procedures, Agile
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Developer, Intern}{Goldman Sachs}{May 2015 -- Aug 2015}		
			\begin{itemize}
				\item Designed and implemented web UI to monitor progress and health of batch jobs by pulling job data from batch processors, determining dependencies, and graphing them.
				\item \underline{Technologies applied} Angular.js, d3.js
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Front End Web Developer}{BYU Broadcasting}{Oct 2013 -- May 2015}		
			\begin{itemize}
				\item Implemented revamped website for BYU Radio.
				\item Implemented new website for BYU TV International.
				\item \underline{Technologies applied} JavaScript, TypeScript, HTML/CSS, Web Components, C\#.NET Razor syntax, jQuery, LESS, handlebars.js, Git, Agile
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
% 	\begin{cvsection}{Software Projects}
% 		\begin{cvsubsection}{}{}{}
% 			\begin{itemize}
% 				\item \textbf{Question Selector} 
% 				\begin{itemize}
% 				    \item Developed simple Python script for selecting random number from a list.
% 				    \item Persistent storage using JSON file.
% 				    \item Argument to the script could be given to remove a retrieved number from the stored list.
% 				    \item \underline{Utilized:} Python
% 				\end{itemize}
% 			\end{itemize}
% 		\end{cvsubsection}
% 	\end{cvsection}
	
	\begin{cvsection}{Skills}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Software} \{proficient\} C\#.NET, Java, JavaScript, TypeScript, Git, HTML/CSS \{familiar\} C, C++, Python, SQL 
				\item \textbf{Frameworks} \{proficient\} ASP.NET Web API, Node.js, React, Redux \{familiar\} Spring Boot, jQuery, Angular.js 1.x
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{document}